### 2020-04-18 writeup/many_tasks_same_covariates.tex
sec 5

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{[\beta_1, \dots, \beta_k] Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

@@

>>>>

\paragraph{Jointly minimizing over all tasks.}
Denote by $\varepsilon(W) = \sum_{i=1}^k \varepsilon_i W_i^{\top}$.
We shall decompose the validation loss $\val(\hat{B}; W_1, \dots, W_k)$ into two parts.
The first part is the model shift bias, which is equal to
\begin{align*}
	\sum_{j=1}^k \bigbrace{\bignorm{\Sigma^{1/2}\bigbrace{\sum_{i=1}^k(\beta_i W_i^{\top}) (ZZ^{\top})^{-1} W_j - \beta_j}}^2}
\end{align*}
The second part is the variance, which is equal to
\begin{align*}
	& \sum_{j=1}^k \exarg{\varepsilon_i, \forall i}{\bigbrace{\bigbrace{\sum_{i=1}^k \varepsilon_i W_i^{\top}} (ZZ^{\top})^{-1} W_j}^2} \cdot {\bigtr{\Sigma(X^{\top}X)^{-1}}} \\
	=& \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}.
\end{align*}
Therefore we shall focus on the minimizer for the model shift bias since the variance part does not depend the weights.
Let us denote $Q\in\real^{k\times k}$ where the $(i,j)$-th entry is equal to $W_i^{\top} (ZZ^{\top})^{-1} W_j$, for any $1\le i, j\le k$.
Let $B^{\star} = [\beta_1, \beta_2, \dots, \beta_k] \in\real^{p \times k}$ denote the true model parameters.
We can now write the validation loss succinctly as follows.
\begin{align*}
	\val(\hat{B}; W_1, \dots, W_k) = \sum_{j=1}^k \bignorm{\Sigma^{1/2} \bigbrace{B^{\star} Q - \beta_j}}^2 + \sigma^2 \cdot \bigtr{\Sigma (X^{\top}X)^{-1}}
\end{align*}
From the above we can solve for $Q$ optimally as \todo{this}.

@@

From the above we can obtain three conceptual insights that are consistent with Section \ref{sec_denoise} and \ref{sec_insight}.
\begin{itemize}
	\item The de-noising effect of multi-task learning.
	\item Multi-task training vs single-task training can be either positive or negative.
	\item Transfer learning is better than the other two. And the improvement over multi-task training increases as the model distances become larger.
\end{itemize}
